Metric conformity

### 2018-08-09 manuscript/supplementary_notes/metric_conformity/assessment.Rmd
update metric characterisation

---
title: "assessment"
output: html_document
params:
  assessment: NULL
---

@@

## `r knitr::include_graphics(rule$image_location)` `r label_long(assessment$rule_id)`

@@

```{r}
width <- ifelse(is.null(assessment$plot_datasets$width), 1, assessment$plot_datasets$width)
height <- ifelse(is.null(assessment$plot_datasets$height), 1, assessment$plot_datasets$height)
```
```{r, fig.width=width, fig.height=height}
assessment$plot_datasets
```

```{r}
width <- ifelse(is.null(assessment$plot_scores$width), 1, assessment$plot_scores$width)
height <- ifelse(is.null(assessment$plot_scores$height), 1, assessment$plot_scores$height)
```
```{r, fig.width=width, fig.height=height}
assessment$plot_scores
```

>>>>

---
title: "assessment"
params:
  assessment: NULL
---

@@

\begin{center}
```{r, out.width="2in", out.height="10in", dpi = 300}
knitr::include_graphics(rule$image_location)
```
\end{center}

@@

A metric conforms to this rule if: $`r rule$conforms_if`$

```{r}
assessment$conformity %>% 
  select(metric_id, conforms) %>% 
  arrange(metric_id) %>% 
  mutate(
    metric_id = label_metrics(metric_id, label_type = "latex") %>% paste0("$", ., "$") %>% forcats::fct_inorder(),
    conforms = kableExtra::cell_spec(
      ifelse(conforms, "\U2714", "\U2716"), 
      background = ifelse(conforms, "#2ECC40", "#FF4136"),
      format = "latex"
    )
  ) %>% 
  spread(metric_id, conforms) %>% 
  knitr::kable(format = "latex", escape = FALSE) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(0, hline_after = FALSE)
```

```{r}
width <- ifelse(is.null(assessment$plot_datasets$width), 1, assessment$plot_datasets$width)
height <- ifelse(is.null(assessment$plot_datasets$height), 1, assessment$plot_datasets$height)
```
```{r A, fig.width=width, fig.height=height, out.width=paste0(width/2, "in")}
assessment$plot_datasets
```

```{r}
width <- ifelse(is.null(assessment$plot_scores$width), 1, assessment$plot_scores$width)
height <- ifelse(is.null(assessment$plot_scores$height), 1, assessment$plot_scores$height)
```
```{r B, fig.width=width, fig.height=height, out.width=paste0(width/2, "in")}
assessment$plot_scores
```

----------------------------------------------------------------------------

\pagebreak

### 2018-08-09 manuscript/supplementary_notes/metric_conformity/metric_conformity.Rmd
update metric characterisation

---
title: "Method conformity"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

```{r}
assessments <- read_rds(derived_file("assessments.rds"))
rules <- read_rds(derived_file("rules.rds"))

rules <- rules %>% 
  mutate(
    image_location = map_chr(id, function(id) figure_file(paste0("images/", id, ".png"))),
    image_found = file.exists(image_location)
  )

if (any(!rules$image_found)) {stop("Files not found: ", basename(rules$image_location[!rules$image_found]))}
```

```{r results='asis'}
walkdf(assessments, function(assessment) {
  cat(knitr::knit_child("assessment.Rmd", quiet=TRUE, envir = environment()))
  cat("\n------------------------------\n")
})
```

>>>>

---
title: "Metric conformity"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
mainfont: DejaVu Sans
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
options(knitr.duplicate.label = 'allow')

@@

```{r}
assessments <- read_rds(derived_file("assessments.rds"))
rules <- read_rds(derived_file("rules.rds"))
```

## Summary

```{r}
assessments %>%
  left_join(rules %>% select(id, name), by = c("rule_id" = "id")) %>%
  unnest(conformity) %>%
  mutate(
    metric_id = label_metrics(metric_id, label_type = "latex") %>% paste0("$", ., "$") %>% forcats::fct_inorder(),
    conforms = kableExtra::cell_spec(
      ifelse(conforms, "\U2714", "\U2716"),
      background = ifelse(conforms, "#2ECC40", "#FF4136"),
      format = "latex"
    )
  ) %>%
  spread(metric_id, conforms) %>%
  select(-rule_id) %>% 
  knitr::kable(format = "latex", escape = FALSE) %>%
  kableExtra::kable_styling(row_label_position = "r")
```

\pagebreak

```{r results='asis'}
# assessment <- dynutils::extract_row_to_list(assessments, 1)

walkdf(assessments[1, ], function(assessment) {
  cat(knitr::knit_child("assessment.Rmd", quiet=TRUE, envir = environment()))
})
```
